A secondary screen architecture to accurately capture TV viewers' interactions and contextual information in TV environments

### 2014-05-05 src/paper.tex
Finished the conclusion

This is paper presents an architecture to accurately capture audience data in interactive TV by using secondary screen devices. The implementation of this architecture is a work in progress and its main goal is to capture viewers' interactions and contextual information to use in applications for interactive TV environments. Potential applications for this data are in the field of content personalization for TV.

Since applications in the TV domain have potential to deal with millions of users at the same time, it is interesting that this CP infrastructure has the ability to handle a growing amount of data~\cite{Lee2010,Kim2012,Shin2009}. The data from millions of viewers obtained from the implementation of this architecture can provide valuable information about viewers. To obtain this information, CPs can employ machine learning algorithms or other techniques on the raw audience data aiming to create viewer profiles for content personalization. As a result, CPs can improve their services aiming to increase the audience or enrich user experience.

>>>>

This is paper presents an architecture to accurately capture audience data in interactive TV by using secondary screen devices. The implementation of this architecture is a work in progress and its main goal is to capture viewers' interactions and contextual information to use in applications for interactive TV environments.

Since applications in the TV domain have the potential to reach out to millions of users at the same time, it is interesting that the CP infrastructure has the ability to deal with a large amount of incoming data~\cite{Lee2010,Kim2012,Shin2009}. The captured data is individual and when it is associated with the context it can provide valuable information about viewers. By using proper machine learning algorithms this data can provide valuable information about viewers. Knowing this information can be very useful for CPs to improve their services aiming to increase the audience and enrich user experience. As an example, CPs can deliver personalized content for a single person as well as for groups of people by using content recommendation algorithms.

The use of personal devices as secondary screens arises as a new trend in TV environments. The architecture described in this paper take advantage of the ubiquity and computational capabilities of secondary screen devices to identify viewers and provide feedback for CPs through viewers' interactions and contextual information.
